### 2017-05-11 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
adding comments to reply letter
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

\begin{quote}
\textcolor{blue}{\textbf{Response:} Here.}
\end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} Here.}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} Here.}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} Here.}
  \end{quote}

  \item Can ESBMC-GPU handle variables in different types of memory?

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} Here.}
  \end{quote}

  \item (Shared, global, thread registers?), and inter-warp communication, for instance?

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} Here.}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} Here.}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} Here.}
  \end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Here.}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Here.}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Here.}
\end{quote}

>>>>

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: haven't we explained that in {\bf Limitations} subsection on page 6?}}
\end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Hussama: could you answer this question? I believe we need the list of properties that each tool can verify and then we can see the differences between them. We should display such information on the website, in addition to the manuscript.}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Isabela: you have more experience with the experimental evaluation. What do you think?}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Isabela: would you be able to tell me that?}}
  \end{quote}

  \item Can ESBMC-GPU handle variables in different types of memory? (Shared, global, thread registers?), and inter-warp communication, for instance?

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: Shall we reference your work about verifying multithread ANSI-C programs?}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Isabela: any insights about coverage?}}
  \end{quote}

@@

  \begin{quote}
  \textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: I didn't get it. Did you?}}
  \end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:}}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: does he mean C++? Shall we reference the paper from ECBS 2013 about ESBMC++?}}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} \textcolor{red}{Lucas: don't we explain that on Functionalities section? Any ideia what else we could add?}}
\end{quote}
